Preregistration analysis, Cost 2 study

### 2019-08-05 Cost2/Cost2_prereg.Rmd
many fixes (see description)
- Fixed duplicate subjid
- Matched survival curves with fixed response times (glitch in logs for few trials)
- Fixed column renaming for OC model. Will now switch all reward columns to the same name across exps.

  # Prep data
  handling <- Data$Handling
  ifelse(is.null(try(dataAll$Offer)), reward <- dataAll$Reward, reward <- dataAll$Offer) #reward <- Data$Offer (FIX THIS BY CALLING ALL COLUMNS REWARD, NOT OFFER)
  choice <- Data$Choice

@@

``` {r Load Data, echo=FALSE}
### data loading and cleaning up
# recent addition: turning forced travels to acceptances, as they reflect a preference for that trial
# rawChoice will be used to compute the # of mistakes
# NOTE: P389 IS DUPLICATED. FIND OUT REAL ID # FOR ONE OF THEM.
setwd("./data")
files <- dir(pattern = '_log.csv')

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  mutate(rawChoice = Choice,
         Choice = ifelse(Choice == 2, 1, Choice),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         optimal = case_when(
          (Handling == 10 & Reward < 8) ~ 0,
          (Handling == 14 & Reward < 20) ~ 0,
          TRUE ~ 1
         ))

@@

autoplot(survData) +
  geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  scale_x_continuous(breaks = seq(14)) +
  ylim(0, 1) +
  labs(x = "Time in Trial", y = "Proportion Completed") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 16))

@@

``` {r 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Compute the OC for pre-midpoint
summaryOC$pre <- dataAll %>%
                 filter(Choice < 2, Half == "Half_1") %>%
                 group_by(Cost, SubjID) %>%
                 do(optimizeOCModel(., simplify = T)) %>%
                 ungroup() %>%
                 select(SubjID, Gamma)

# let's add the gammas to the second half data and estimate prop predicted on the second half
summaryOC$predicted <- dataAll %>%
                 filter(Choice < 2, Half == "Half_2") %>%
                 group_by(Cost, SubjID) %>%
                 left_join(summaryOC$pre) %>%
                 mutate(OC = Handling * Gamma,
                        predicted = Reward > OC) %>% 
                 summarise(percentPredicted = mean(predicted == Choice) * 100)

>>>>

  # Prep data
  handling <- Data$Handling
  reward <- Data$Offer 
  choice <- Data$Choice

@@

``` {r Load Data, echo=FALSE}
### data loading and cleaning up
# recent addition: turning forced travels to acceptances, as they reflect a preference for that trial
# rawChoice will be used to compute the # of mistakes
# The RT is upper-bounded because a glitch in the code made two 14s trials last longer (among all p's) 
setwd("./data")
files <- dir(pattern = '_log.csv')

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  mutate(rawChoice = Choice,
         RT = ifelse(RT > 14.1, 14, RT),
         Choice = ifelse(Choice == 2, 1, Choice),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         optimal = case_when(
          (Handling == 10 & Reward < 8) ~ 0,
          (Handling == 14 & Reward < 20) ~ 0,
          TRUE ~ 1
         ))

@@

autoplot(survData) +
  geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  scale_x_continuous(breaks = seq(14)) +
  ylim(0, 1) +
  labs(x = "Time in Trial", y = "Proportion Completed", fill = "Cost", color = "Cost") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 16))

@@

``` {r 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Compute the OC for pre-midpoint
summaryOC$pre <- dataAll %>%
                 filter(Choice < 2, Half == "Half_1") %>%
                 rename(Offer = Reward) %>%
                 group_by(Cost, SubjID) %>%
                 do(optimizeOCModel(., simplify = T)) %>%
                 ungroup() %>%
                 select(SubjID, Gamma)

# let's add the gammas to the second half data and estimate prop predicted on the second half
summaryOC$predicted <- dataAll %>%
                 filter(Choice < 2, Half == "Half_2") %>%
                 rename(Offer = Reward) %>%
                 group_by(Cost, SubjID) %>%
                 left_join(summaryOC$pre) %>%
                 mutate(OC = Handling * Gamma,
                        predicted = Offer > OC) %>% 
                 summarise(percentPredicted = mean(predicted == Choice) * 100)
